% resume.tex
% vim:set ft=tex spell:

\documentclass[10pt,letterpaper]{article}
\usepackage[letterpaper,margin=0.75in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{mdwlist}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage{tgpagella}
\pagestyle{empty}
\setlength{\tabcolsep}{0em}

% indentsection style, used for sections that aren't already in lists
% that need indentation to the level of all text in the document
\newenvironment{indentsection}[1]%
{\begin{list}{}%
	{\setlength{\leftmargin}{#1}}%
	\item[]%
}
{\end{list}}

% opposite of above; bump a section back toward the left margin
\newenvironment{unindentsection}[1]%
{\begin{list}{}%
	{\setlength{\leftmargin}{-0.5#1}}%
	\item[]%
}
{\end{list}}

% format two pieces of text, one left aligned and one right aligned
\newcommand{\headerrow}[2]
{\begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
	#1 &
	#2 \\
\end{tabular*}}

% make "C++" look pretty when used in text by touching up the plus signs
\newcommand{\CPP}
{C\nolinebreak[4]\hspace{-.05em}\raisebox{.22ex}{\footnotesize\bf ++}}

% and the actual content starts here
\begin{document}

\begin{center}
{\LARGE \textbf{David A. Wang}}

3465 Sansom Street MB270\ \ \textbullet
\ \ Philadelphia, PA 19104
\\
(949) 276-3804\ \ \textbullet
\ \ david@dwang.org
\end{center}


\hrule
\vspace{-0.4em}
\subsection*{Objective}
\begin{indentsection}{\parindent}
\begin{description*}
	\item Self-taught Django/python hacker with a special knack for UI, looking for an internship/startup opportunity.
\end{description*}
\end{indentsection}

\hrule
\vspace{-0.4em}
\subsection*{Experience}

\begin{itemize}
	\parskip=0.1em

	\item
	\headerrow
		{\textbf{MobLaundry}}
		{\textbf{www.moblaundry.com}}
	\\
	\headerrow
		{\emph{Co-founder and UI/Backend Developer}}
		{\emph{January 2011}}
	\begin{itemize*}
		\item Mobile application to allow college students easily check their laundry status via web or text.
		\item Crafted mobile frontend using HTML5 \& CSS3 and backend in Python, Django, and MySQL.
		\item API written with Django-Piston and web service deployed using Fabric, \& Buildout, \& Pip.
	\end{itemize*}


	\item
	\headerrow
		{\textbf{Nanobio Interface Center - Nanoprobe Network}}
		{\textbf{www.nanoprobenetwork.org, UPenn}}
	\\
	\headerrow
		{\emph{Web Consultant, collaborated with Mr. Praetzel }}
		{\emph{2009 - Present}}
	\begin{itemize*}
		\item Introduced caching to the old web firm to resolve a critical live forum crashing issue when more than 15 people/sec tried to visit the site.
		\item Utilized a more user discussion driven approach to a new site redesign to increase traffic by 20\% and reduced site loading times from 5s to 1s.
	\end{itemize*}



	\item
	\headerrow
		{\textbf{College House of Computing}}
		{\textbf{University of Pennsylvania, PA}}
	\\
	\headerrow
		{\emph{Senior Information Technology Assistant (Sr. ITA)}}
		{\emph{2009 -- Present}}
	\begin{itemize*}
		\item Regreased and disassembled entire laptops; removed rootkits, malware, and other computer issues. 
		\item Wrote and held annual security themed hacking contests to raise awareness about computer security in Kings Court: (dwang.org/projects/kingscourt)
	\end{itemize*}

	\item
	\headerrow
		{\textbf{Engineering Student Activities Council}}
		{\textbf{University of Pennsylvania, PA}}
	\\
	\headerrow
		{\emph{Tech}}
		{\emph{2010-Present}}
	\begin{itemize*}
		\item Built a dynamic jQuery plugin to facilitate selection of financial forms. Demo: (dwang.org/projects/esac)
	\end{itemize*}


	\item
	\headerrow
		{\textbf{"Modeling Physical Phenomena Using Computation"}}
		{\textbf{UCLA, CA}}
	\\
	\headerrow
		{\emph{Summer Researcher, mentored by UCLA researchers Scott Friedman and Shao Ching Huang }}
		{\emph{Summer 2008}}
	\begin{itemize*}
		\item Implemented molecular dynamics simulation code in C and utilized Newton's 3rd law to optimize the simulation code and reduce the number of force calculations by half.
		\item Utilized OpenMP to parallelize the forces calculations in the simulation code.
		\item Created kinetic energy and velocity distribution plots to validate the dynamic equilibrium system state.
	\end{itemize*}

\end{itemize}


\hrule
\vspace{-0.4em}
\subsection*{Other Projects}

\begin{indentsection}{\parindent}
\hyphenpenalty=1000
\begin{description*}
	\item[TV-B-Gone Converter:] Built an translator to accept Pronto IR codes to allow the TV-B-Gone to control projectors.
	\item[Aliso Niguel NHS:] Built a multi-user system to handle shift swapping, messaging system, and blog posts.
	\item[Pinkoman:] 200+ line bash script for Macs that analyzes user behavior and prevents unintended activity.
	\item[ANHS:] Security Advisor - uncovered numerous XSS holes, directory traversal attacks, SQL injections.
\end{description*}
\textit{More details can be found at: http://www.dwang.org/projects} 
\end{indentsection}


\hrule
\vspace{-0.4em}
\subsection*{Education}

\begin{itemize}
	\parskip=0.1em

	\item 
	\headerrow
		{\textbf{University of Pennsylvania}}
		{\textbf{Philadelphia, PA}}
	
	\headerrow
		{\emph{School of Engineering and Applied Science, B.S.E Bioengineering}}
		{\emph{2009 -- 2013}}
	\begin{itemize*}
		\item Minor: Computer Science and Nanotechnology
	\end{itemize*}

\end{itemize}


\hrule
\vspace{-0.4em}
\subsection*{Core Technical Skills}

\begin{indentsection}{\parindent}
\hyphenpenalty=1000
\begin{description*}
	\item[Languages:]
	C, Java, OCaml, JavaScript, PHP, MySQL, Python, Django, HTML5, CSS3, shell scripting
	\item[Software:] Final Cut Pro, Adobe Photoshop, Adobe Illustrator
\end{description*}
\end{indentsection}

\end{document}
